R for Clinical Study Reports and Submission

### 2021-11-09 project-management.Rmd
rename `adam_data/` as `data-adam/`
update project folder

> After project initiation, modifying `.Rprofile` will be a risk of reproducibility
> and should be handled carefully if necessary.

@@

The analysis code and relevant description can be saved in R Markdown files
in the `vignettes` folder.

>>>>

::: {.rmdnote}
After project initiation, modifying `.Rprofile` will be a risk of reproducibility
and should be handled carefully if necessary.
:::

@@

The analysis code and relevant description can be saved in R Markdown files
in the `vignettes/` folder.
